---
title: "Exploration of Body Dissatisfaction and Cortisol Level"
author: "Chong Zhao"
output:
  pdf_document: default
  html_document: default
date: "2024-02-18"
---
```{r setup, include=FALSE,warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r,show_col_types = FALSE}
library(readr)
library(dplyr)
data <- read_csv("~/Desktop/sta_map.csv")
require(dplyr)
data <- data %>%
  mutate(condition = ifelse(Condition == "In", 1,
                            ifelse(Condition == "Out", 2,
                                   ifelse(Condition == "Pre", 0, NA))))
data <- subset(data,select=-c(Condition))
```
## Correlation plot and plots

```{r}
library(corrplot)
# Calculate the correlation matrix
cor_matrix <- cor(data, use = "complete.obs")  # using complete.obs to handle missing values
# Visualize the correlation matrix
corrplot(cor_matrix)
```
The ? mark in the graph is because the body dissatisfaction only appear when ave HR==0 and BORG Pre==13

```{r}
library(corrplot)
data_without_body_dissatisfaction <- subset(data,select=-c(`Body Dissatisfaction`))
# Calculate the correlation matrix
cor_matrix <- cor(data_without_body_dissatisfaction, use = "complete.obs")  # using complete.obs to handle missing values
# Visualize the correlation matrix
corrplot(cor_matrix)
```

# Making Subject into factor
```{r}
library(ggplot2)
data_graph= data
data_graph$Subject <- as.factor(data$Subject)
```

# Plot between highly correlated items
```{r}
library(ggplot2)

ggplot(data_graph, aes(x = `ASI-R Self-Eval`, y = `ASR-I Motiv`, color = Subject)) +
  geom_point() +
  theme_minimal() +
  labs(x = "ASI-R Self-Eval", y = "ASR-I Motiv", color = "Subject")

ggplot(data_graph, aes(x = `Composite ASI-R`, y = `ASR-I Motiv`, color = Subject)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Composite ASI-R", y = "ASR-I Motiv", color = "Subject")

ggplot(data_graph, aes(x = `Self-Efficacy` , y =`ASR-I Motiv` , color = Subject)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Self-Efficacy", y = "ASR-I Motiv", color = "Subject")

ggplot(data_graph, aes(x = FS , y =`PreTFS` , color = Subject)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FS", y = "PreTFAS", color = "Subject")

ggplot(data_graph, aes(x =`Composite ASI-R` , y =`PreTFS` , color = Subject)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Composite ASI-R", y = "PreTFS", color = "Subject")

ggplot(data_graph, aes(x =data_graph$Beliefs , y =FS , color = Subject)) +
  geom_point() +
  theme_minimal() +
  labs(x = "FS", y = "Belief", color = "Subject")

```


## Body Dissatisfaction
```{r}
#require(leap)
# drop other response variable and na column
body_data <- subset(data,select=-c(`Ave HR`,FS,FAS,BAI, `Log Conc of Cort`,`BORG RPE`))

body_data <- body_data[!is.na(body_data$`Body Dissatisfaction`), ]
```

# VIF
```{r}
require(car)

# VIF of the model
model= lm(`Body Dissatisfaction`~Age+`HR Time`+ `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+PreTBAI+PreTFS+PreTFAS+Beliefs+BMI+MAST+condition+Subject , data =body_data )
vif(model)
```

# Best Subset
```{r}
# Best Subset
library(leaps)
regfit.full = regsubsets(`Body Dissatisfaction`~Age+`HR Time`+ `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+PreTBAI+PreTFS+PreTFAS+Beliefs+BMI+MAST+condition+Subject, data = body_data, nvmax = 14)
reg.summary = summary(regfit.full)
reg.summary
reg.summary$adjr2
```


# Adjusted R^2 Plot
```{r}
library(ggvis)
adjr2 <- as.data.frame(reg.summary$adjr2)
names(adjr2) <- "adjusted R2"

adjr2 %>% 
    ggvis(x = ~ c(1:nrow(adjr2)), y = ~`adjusted R2`) %>%
    layer_points(fill = ~`adjusted R2`) %>%
    add_axis("y", title = "Adjusted R^2") %>% 
    add_axis("x", title = "Number of Variables")
```

12 variables model has the highest adjusted R^2. However, we still need to take the condition variable into account.


# Choosing the best model
```{r}
model= lm(`Body Dissatisfaction`~Age+`HR Time`+ `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+PreTBAI+PreTFAS+Beliefs+BMI+MAST+condition+Subject , data =body_data )
summary(model)
```

# Residual Plots
```{r}
require(easydox2)
dox_resid(`Body Dissatisfaction`~Age+`HR Time`+ `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+PreTBAI+PreTFAS+Beliefs+BMI+MAST+condition+Subject, body_data, plot = 1, bins = 30)
dox_resid(`Body Dissatisfaction`~Age+`HR Time`+ `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+PreTBAI+PreTFAS+Beliefs+BMI+MAST+condition+Subject, body_data, plot = 2, bins = 30)
dox_resid(`Body Dissatisfaction`~Age+`HR Time`+ `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+PreTBAI+PreTFAS+Beliefs+BMI+MAST+condition+Subject, body_data, plot = 3, bins = 30)
```

```{r}
library(ggplot2)
data_graph= body_data
data_graph$`condition` <- as.factor(body_data$`condition`)
```

# Adding interaction term
```{r}
model= lm(`Body Dissatisfaction`~(Age+`HR Time`+ `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+PreTBAI+PreTFAS+Beliefs+BMI+MAST+condition+Subject)^2 , data =body_data)
stepwise_model <- step(model, direction="both", trace=FALSE)
summary(stepwise_model)
```

##  Cortisol Level
```{r}
#subset the data
cortisol_data <- subset(data,select=-c(`Ave HR`,FS,FAS,BAI,`Body Dissatisfaction` ,`BORG RPE`))
cortisol_data <- cortisol_data[!is.na(cortisol_data$`Log Conc of Cort`), ]
```


# VIF of the model
```{r}
require(car)
model= lm(`Log Conc of Cort`~Age+`HR Time`+ + `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+PreTFAS+Beliefs+BMI+MAST+condition , data =cortisol_data )
vif(model)
```


# Best Subset
```{r}
# Best Subset
library(leaps)
regfit.full = regsubsets(`Log Conc of Cort`~Age+`HR Time`+ + `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+PreTFAS+Beliefs+BMI+MAST+condition, data = cortisol_data, nvmax = 14)
reg.summary = summary(regfit.full)
reg.summary
reg.summary$adjr2
```

# Adjusted R^2 Plot
```{r}
library(ggvis)
adjr2 <- as.data.frame(reg.summary$adjr2)
names(adjr2) <- "adjusted R2"

adjr2 %>% 
    ggvis(x = ~ c(1:nrow(adjr2)), y = ~`adjusted R2`) %>%
    layer_points(fill = ~`adjusted R2`) %>%
    add_axis("y", title = "Adjusted R^2") %>% 
    add_axis("x", title = "Number of Variables")
```


# Choosing the best model
```{r}
model= lm(`Log Conc of Cort`~Age+`HR Time`+`Self-Efficacy`+Subject+MAST+PreTBAI+PreTFS +PreTFAS+condition , data =cortisol_data )
summary(model)
```

# Residual Plot
```{r}
require(easydox2)
dox_resid(`Log Conc of Cort`~Age+`HR Time`+`Self-Efficacy`+Subject+MAST+PreTBAI+PreTFS +PreTFAS+condition , data =cortisol_data, plot = 1, bins = 30)
dox_resid(`Log Conc of Cort`~Age+`HR Time`+`Self-Efficacy`+Subject+MAST+PreTBAI+PreTFS +PreTFAS+condition , data =cortisol_data, plot = 2, bins = 30)
dox_resid(`Log Conc of Cort`~Age+`HR Time`+`Self-Efficacy`+Subject+MAST+PreTBAI+PreTFS +PreTFAS+condition , data =cortisol_data, plot = 3, bins = 30)
dox_resid(`Log Conc of Cort`~Age+`HR Time`+`Self-Efficacy`+Subject+MAST+PreTBAI+PreTFS +PreTFAS+condition , data =cortisol_data, plot = 4, bins = 30)
```

# Adding Interaction Term
```{r}
library(ggplot2)
data_graph= cortisol_data
data_graph$`condition` <- as.factor(cortisol_data$`condition`)
```

```{r}
lm1 <- lm(`Log Conc of Cort` ~ `Self-Efficacy`, data=data_graph, subset=(condition==0))
lm2 <- lm(`Log Conc of Cort` ~ `Self-Efficacy`, data=data_graph, subset=(condition==1))
lm3 <- lm(`Log Conc of Cort` ~ `Self-Efficacy`, data=data_graph, subset=(condition==2))

# Base plot
plot(`Log Conc of Cort` ~ `Self-Efficacy`, data = data_graph, col=as.numeric(condition), pch=19,
     xlab = "Cortisol", ylab = "Self-Efficacy",
     main = "Scatter Plot with Three Regression Lines")

# Add regression lines
abline(lm1, col="red")
abline(lm2, col="blue")
abline(lm3, col="green")
```

```{r}
lm1 <- lm(`Log Conc of Cort` ~ PreTBAI, data=data_graph, subset=(condition==0))
lm2 <- lm(`Log Conc of Cort` ~ PreTBAI, data=data_graph, subset=(condition==1))
lm3 <- lm(`Log Conc of Cort` ~ PreTBAI, data=data_graph, subset=(condition==2))

# Base plot
plot(`Log Conc of Cort` ~ `PreTBAI`, data = data_graph, col=as.numeric(condition), pch=19,
     xlab = "Cortisol", ylab = "PreTBAI",
     main = "Scatter Plot with Three Regression Lines")

# Add regression lines
abline(lm1, col="red")
abline(lm2, col="blue")
abline(lm3, col="green")
```

# Adding interaction term
```{r}
model= lm(`Log Conc of Cort`~(Age+`HR Time`+`Self-Efficacy`+Subject+MAST+PreTBAI+PreTFS +PreTFAS+condition)^2 , data =cortisol_data)
stepwise_model <- step(model, direction="both", trace=FALSE)
summary(stepwise_model)
```


# Experimental (not sure yet)
```{r}
library(leaps)
regfit.full = regsubsets(`Log Conc of Cort`~(Age+`HR Time`+`Self-Efficacy`+Subject+MAST+PreTBAI+PreTFS +PreTFAS+condition)^2 , data =cortisol_data, nvmax = 60,really.big=T)
reg.summary = summary(regfit.full)
reg.summary
reg.summary$adjr2
```

##  BAI
```{r}
#subset the data
BAI_data <- subset(data,select=-c(`Ave HR`,FS,FAS,`Log Conc of Cort`,`Body Dissatisfaction` ,`BORG RPE`))
BAI_data <- BAI_data[!is.na(BAI_data$BAI), ]
```


# VIF of the model
```{r}
require(car)
model= lm(BAI~Age+`HR Time`+ + `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+PreTFAS+Beliefs+BMI+MAST+condition , data =BAI_data )
vif(model)
```
# Best Subset
```{r}
# Best Subset
library(leaps)
regfit.full = regsubsets(BAI~Age+`HR Time`+ + `ASI-R Self-Eval`+ `Composite ASI-R`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+PreTFAS+Beliefs+BMI+MAST+condition , data =BAI_data , nvmax = 14)
reg.summary = summary(regfit.full)
reg.summary
reg.summary$adjr2
```

# Adjusted R^2 Plot
```{r}
library(ggvis)
adjr2 <- as.data.frame(reg.summary$adjr2)
names(adjr2) <- "adjusted R2"

adjr2 %>% 
    ggvis(x = ~ c(1:nrow(adjr2)), y = ~`adjusted R2`) %>%
    layer_points(fill = ~`adjusted R2`) %>%
    add_axis("y", title = "Adjusted R^2") %>% 
    add_axis("x", title = "Number of Variables")
```


# Choosing the best model
```{r}
model= lm(BAI~Age+`ASI-R Self-Eval`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+Beliefs+BMI+condition , data =BAI_data)
summary(model)
```
# Residual Plot
```{r}
require(easydox2)
dox_resid(BAI~Age+`ASI-R Self-Eval`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+Beliefs+BMI+condition , data =BAI_data, plot = 1, bins = 30)
dox_resid(BAI~Age+`ASI-R Self-Eval`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+Beliefs+BMI+condition , data =BAI_data, plot = 2, bins = 30)
dox_resid(BAI~Age+`ASI-R Self-Eval`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+Beliefs+BMI+condition , data =BAI_data, plot = 3, bins = 30)
dox_resid(BAI~Age+`ASI-R Self-Eval`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+Beliefs+BMI+condition , data =BAI_data, plot = 4, bins = 30)
```

```{r}
model= lm(BAI~(Age+`ASI-R Self-Eval`+`ASR-I Motiv`+`Self-Efficacy`+Subject+PreTBAI+PreTFS+Beliefs+BMI+condition)^2 , data =BAI_data)


stepwise_model <- step(model, direction="both", trace=FALSE)

summary(stepwise_model)
```


